Marshall and Olkin-G and Gamma-G family of distribution: properties and applications

### 2022-05-25 paper/reviews/answers/Reply_Letter_May_24.tex
Add TTT plots.

\documentclass[version=last,12pt,{"maintainersDelight"},letterpaper,]{scrlttr2}

@@

\begin{letter}{\textbf{Replies to reviewers}\\\textbf{REVSTAT}\\}
\opening{Dear \textbf{REVSTAT} Executive Editor and Reviews,}

in this letter, I will respond to each of the reviewers valuable
contributions. We try to accept all suggestions, aiming at a significant
improvement of our article. After each questioning, the respective
answers will be given. As suggested by the second reviewer, the title of
the paper was modified and better represents the proposal of the work.

@@

@@

\emph{Response}:
\textcolor{red}{Indeed, the way in which the application section was introduced suggests that an attempt was made to fit the $G\sim Weibull$ model as a suitable distribution to the current datasets. In order to remove some ambiguity, we opted to extend the simulation studies, where we now include the $G\sim Weibull$ in the simulations.}

@@

\emph{Response}:
\textcolor{red}{Thank you for pointing that out. The Dagum distribution was now included in Table 1.}

@@

\emph{Response}:
\textcolor{red}{The use of the Anderson-Darling  $A^*$ and Cram\'er-von Mises $W^*$  statistics, corrected by Chen and Balakrishnan, in the paper entitled ``A General Purpose Approximate Goodness-of-Fit Test'' (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) is indicated for comparing mo\-dels that are not necessarily embedded. Hence, considering the statistics returned by the \texttt{goodness.fit} function and the distributions compared, we understand that these statistics are the most suitable ones for 
the comparisons.}

@@

13 -- I suggest to make the labels of Figure 1 and of tables in \LaTeX, not in R.

\emph{Response}:
\textcolor{red}{Thanks for the suggestion. The change suggestion has been implemented.}

@@

3 - The bibliography does not have many recent publications such as
Martinez-Florez et al. (2020) and Magalhaes et al.~(2020). I also
suggest authors to create the state-of-art related to this topic in the first section that definitively needs to be improved.

@@

@@

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \tightlist
  \item
    \textcolor{red}{ Really, the title of the paper was no good. We changed to \textbf{Marshall and Olkin-Gamma-G family of distributions: properties and applications}. We believe that the title now clarifies the paper's proposal better. It is worth mentioning that the new name is consistent with the sequential application of the MO family to the baseline Gamma-G.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \textcolor{red}{Done. Thanks for the suggestion.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{2}
  \tightlist
  \item
    \textcolor{red}{Thanks for this point. The presentation of the tables was reorganized.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{3}
  \tightlist
  \item
    \textcolor{red}{Thanks for the suggestion. We chose to put the code for the simulations in a repository on GitHub. Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code. With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained. To access the codes, see the link 
    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
  \end{enumerate}
\end{itemize}

>>>>

\documentclass[version=last,12pt,{"maintainersDelight"}]{scrlttr2}

@@

\begin{letter}{\textbf{Replies to reviewers' comments}\\\textbf{REVSTAT}\\}
\opening{Dear Executive Editor and Reviews,}

In this letter, we will answer to each of the reviewers valuable
contributions. We try to accept all suggestions, aiming at a significant
improvement of our article. After each questioning, the respective
answers will be given. As suggested by the second reviewer, the title of
the paper was modified and better represents the proposal of the work.

@@

\emph{Response}: \textcolor{red}{Thank you. Done}.

@@

\emph{Response}:
{\color{red} Indeed, the way in which the application section was introduced suggests that a forced attempt was made to fit the $G\sim Weibull$ model as an adequate distribution to the datasets, thus clashing with the distribution considered in the simulations. To eliminate some ambiguity, we chose to extend the simulations studies, where we now also include the MOGa-Weibull distribution.

Furthermore, the simulations of the MOGa-Dagum distribution were redone, considering that the current hardware is not 
the same as that one we used at the time of submission.

The Monte-Carlo simulations were performed in parallel, using the package \textbf{parallel} of the \texttt{R} language, in which the pseudo-random number generator considered for a processing with thread division was the L'Ecuyer-CMRG (see \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.47.1.159} and \url{https://pubsonline.informs.org/doi/abs/10.1287/opre.50.6.1073.358}. As this generator depends on a fixed seed and also on the number of threads, which in turn depends on the hardware used, this was the other reason that led us to redo all the simulations.}

@@

\emph{Response}:
\textcolor{red}{Thank you for pointing that out. The Dagum distribution is now included in Table 1.}

@@

\emph{Response}:
\textcolor{red}{The use of the Anderson-Darling  A$^*$ and Cram\'er-von Mises W$^*$  statistics, corrected by Chen and Balakrishnan, in the paper entitled ``A General Purpose Approximate Goodness-of-Fit Test'' (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) is indicated for comparing mo\-dels that are not necessarily embedded. Hence, considering the statistics returned by the \texttt{goodness.fit} function and the distributions compared, we understand that these statistics are the most suitable ones for 
the comparisons.}

@@

13 -- I suggest to make the labels of Figure 1 and of tables in \LaTeX, not in \texttt{R}.

\emph{Response}:
\textcolor{red}{Thanks for the suggestion. This suggestion was implemented.}

@@

3 - The bibliography does not have many recent publications such as
Martinez-Florez et al. (2020) and Magalhães et al.~(2020). I also
suggest authors to create the state-of-art related to this topic in the first section that definitively needs to be improved.

@@

\emph{Response}: \textcolor{red}{Missing.}

@@

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \tightlist
  \item
    \textcolor{red}{Really, the title of the paper was no good. We changed to \textbf{The Marshall and Olkin-Gamma-G family of distributions: properties and applications}. We believe that the title now clarifies the paper's proposal better. It is worth mentioning that the new title is very consistent with the sequential application of the MO family to the baseline Gamma-G.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \textcolor{red}{Done. Thanks for the suggestion.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{2}
  \tightlist
  \item
    \textcolor{red}{Thanks for this point. The presentation of the tables was reorganized.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{3}
  \tightlist
  \item
    \textcolor{red}{Thanks for the suggestion. We chose to put the code for the simulations in a repository on GitHub. Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code. With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained. To access the codes, see the link 
    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
  \end{enumerate}
\end{itemize}
